Empirical pipeline

### 2024-11-27 Analysis/03_Empirical_pipeline.Rmd
Update 03_Empirical_pipeline.Rmd

>>>>

## Empirical example for box 2

```{r}
library(dispRity)
## Plotting the trait space
data <- custom.subsets(empirical_traitspace, group = lapply(groups, which))
pdf(file = "../Manuscript/Figures/empirical_example.pdf", height = 4, width = 4)
plot(data, legend = FALSE, col = c("blue", "orange"))
legend("topright", pch = 19, col = c("blue", "orange"), legend = c("Current species", "Species in 1500"))
dev.off()

## Measuring disparity
library(xtable)
xtable(summary(dispRity(data, metric = convhull.volume)))
xtable(summary(dispRity(data, metric = displacements)))
```

## Empirical number of dimensions selection

```{r}
library(dispRity)
pca <- readRDS("../Data/Processed/pca-object-historic-community.RDS")
data <- custom.subsets(pca$x, group = list(extant = extant_species, at_1500 = historic_species))
pdf(file = "../Manuscript/Figures/empirical_data_dimensions.pdf", height = 8, width = 4)
plot(select.axes(data))
dev.off()
```
